Object Naming in Language and Vision: A Survey and a New Dataset

### 2019-11-25 papers/LREC2020/analysis.tex
some changes towards the LREC submission
Section 4 - data collection polished

\gbt{I think that we will need to remove the class-based analysis, for lack of space (plus, I think that the instance-level analysis is enough to get an idea of the data). For the moment I'm not doing it because I'd like to have your ok first. If we don't, we need to give an example and also say how many classes we have. Also, maybe rename ``\vg synsets'' instead of ``class''?}
\gbt{BEGIN PART NOT EDITED}
We use the following annotations for each object: (i) the original name, annotated in \vg, (ii) the object class or synset, annotated in \vg\footnote{Recall that we used these VG synsets for collecting our images (Section~\ref{ssec:sampling})},
%and obtained via a semi-automatic linking of the object name to WordNet
 (iii) the ManyNames response set, i.e. a set of name types with annotation frequencies (max. 36 annotations per object),  see Figure \ref{fig:ex-high-low-agreement} for examples.
 % of objects and their response sets (top rows below the images).
 %[if model preds are kept]}. 
 Based on the \vg synsets, we aggregate the annotations for instances of the same class and obtain a class-level response set that contains all names and their frequencies annotated for all objects of a class.

@@

We did qualitative analysis and found the following types of variation in the data, illustrated with examples in Figure~\ref{fig:ex-high-low-agreement}.
\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog}).
\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}). 
\textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose synonyms or hypernyms (\textit{robe-dress}).
%As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
%
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{2pt}
\begin{tabular}{lcc|p{2.5cm}}
\toprule
         relation & \% types & \% token & \it ex: jacket \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 word-not-covered &  10.6 &  2.6 & \it outdoor vest\\
\midrule
 synonym &  1.1 &  1.1 & \it hoodie  \\
 hyponym &  2.2 &  3.8 & \it parka, blazer \\
 co-hyponym &  3.1 &  5.9 & \it raincoat\\
 hypernym &  10.5 &  27.7 & \it clothing, coat\\
 rel-not-covered &  72.2 &  58.3 & \it sweatshirt, man\\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets. \gbt{TO DO (IMPORTANT): change the rel-not-covered example to something that is true naming variation. I moved referential uncertainty out of the analysis of sources of variation.}}
\label{tab:rel}
\vspace{-0.5cm}
\end{table}

>>>>

\gbt{I think that we will need to remove the class-based analysis, for lack of space (plus, I think that the instance-level analysis is enough to get an idea of the data). For the moment I'm not doing it because I'd like to have your ok first. If we don't, we need to give an example and also say how many classes we have. Also, maybe rename ``\vg synsets'' instead of ``class''?} \sz{yes, please remove the class-based analysis. it's probably rather confusing}
\gbt{BEGIN PART NOT EDITED}
We use the following annotations for each object: (i) the original name, annotated in \vg, (ii) the object class or synset, annotated in \vg\footnote{Recall that we used these VG synsets for collecting our images (Section~\ref{ssec:sampling})},
%and obtained via a semi-automatic linking of the object name to WordNet
 (iii) the ManyNames response set, i.e. a set of name types with annotation frequencies (max. 36 annotations per object),  see Figure \ref{fig:ex-high-low-agreement} for examples.
 % of objects and their response sets (top rows below the images).
 %[if model preds are kept]}. 
 Based on the \vg synsets, we aggregate the annotations for instances of the same class and obtain a class-level response set that contains all names and their frequencies annotated for all objects of a class.

@@

We did qualitative analysis and found the following types of variation in the data, illustrated with examples in Figure~\ref{fig:ex-high-low-agreement}.
\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog}).
\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}). 
\textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose synonyms or hypernyms (\textit{robe-dress}).
%As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
%
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{2pt}
\begin{tabular}{lcc|p{2.5cm}}
\toprule
         relation & \% types & \% token & \it ex: jacket \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 word-not-covered &  10.6 &  2.6 & \it outdoor vest\\
\midrule
 synonym &  1.1 &  1.1 & \it hoodie  \\
 hyponym &  2.2 &  3.8 & \it parka\\ %, blazer \\
 co-hyponym &  3.1 &  5.9 & \it raincoat\\
 hypernym &  10.5 &  27.7 & \it clothing \\%, coat\\
 rel-not-covered &  72.2 &  58.3 & \it sweatshirt\\%, man\\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets, with examples.}
\label{tab:rel}
\vspace{-0.5cm}
\end{table}

### 2019-11-25 papers/LREC2020/data-collection.tex
Section 4 - data collection polished

\begin{table*}[htp]
	\small
	\centering
	\begin{tabular}{lp{14cm}}
			\toprule
			Domain & \multicolumn{1}{c}{Synsets}\\
			\midrule			
			buildings      &  house$_1$ (364), bridge$_1$ (297), shelter$_1$ (169), restaurant$_1$ (58),
                                         outbuilding$_1$ (31), hotel$_1$ (19), housing$_1$ (17), place\_of\_worship$_1$ (12)     \\
			people         & woman$_1$ (1768), man$_1$ (1167), male\_child$_1$ (853), athlete$_1$ (396),
			 child$_1$ (333), creator$_2$ (11), professional$_1$ (5)    \\
			home           &  furnishing$_2$ (5,355), vessel$_3$ (525), kitchen\_utensil$_1$ (132), crockery$_1$ (92),
			cutlery$_2$ (82), tool$_1$ (72), lamp$_1$ (34)    \\
			clothing       &  shirt$_1$ (968), overgarment$_1$ (786), dress$_1$ (199), headdress$_1$ (135),
                                         neckwear$_1$ (65), robe$_1$ (27), glove$_2$ (7), footwear$_1$ (5)    \\
			vehicles       &  aircraft$_1$ (1208), train$_1$ (957), car$_1$ (727), motorcycle$_1$ (564),
                                         truck$_1$ (559), boat$_1$ (499), ship$_1$ (38)    \\
			food           &  dish$_2$ (812), baked\_goods$_1$ (770), foodstuff$_2$ (280), vegetable$_1$ (48),
                                         edible\_fruit$_1$ (42), beverage$_1$ (23)   \\
			animals\_plants & ungulate$_1$ (2037), horse$_1$ (833), feline$_1$ (763), dog$_1$ (688)
			bird$_1$ (389), flower$_1$ (44), rodent$_1$ (27), insect$_1$ (12), fish$_1$ (11)\\
			\bottomrule
		\end{tabular}
		\caption{Overview of the ManyNames dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses).
                  \label{tab:overview_dataset2}}
	\end{table*}

@@

We take data from \vgenome~\cite{krishna2016visualgenome}, which
contains a dense region-based labeling of $108$K~images with, inter alia, object names, attributes and relationships,
all linked to WordNet synsets \cite{fellbaum1998wordnet}.
\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
As common in Computer Vision, objects are localized as bounding boxes, as in Figure~\ref{fig:cake}.% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

@@

%Criteria: From CV: select images depicting objects with relatively frequent names; From CogSci: select objects which have been frequently studied in cognitive science/psychological norming studies; we chose McRae et al. as basis.
We selected images from seven domains: six based on McRae et al.'s  (\cite{mcrae2005semantic}) feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is a very frequent category in \vg.
% We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
% We added the \textsc{person} category because it is very frequent category in \vgenome.

Within each domain, we aimed at collecting instances at different taxonomic levels to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy in the first place (e.g.\ \textsc{home}).
Instead, we defined a set of synsets ($52$\ in total; listed in Table~\ref{tab:overview_dataset2}) that we used to collect our object instances from \vg.

From the set of synsets that match or subsume the concepts in the McRae norms, we kept those with a high number of \vg object instances of different names.
For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}

We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds} ($450$\ in total).
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.} 
% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
% \paragraph{Sampling of instances}
Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds. This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as follows.
Table~\ref{tab:overview_dataset1} shows the top 5 \vgenome names in each of the domains.
% \begin{itemize}
% \item rows: domains (if we go for long paper: then one row per collection node?)
% \item columns:
%   \begin{enumerate}
%   \item \# collection nodes
%   \item collection nodes (list)
%   \item \# unique VG names
%   \item example VG names
%   \item \# unique objects
%   \item \# unique images (? not sure if necessary; maybe only one of unique {objects, images})
%   \end{enumerate}
% \end{itemize}

@@

To elicit object names, we set up a crowdsourcing task on Amazon Mechanical Turk (AMT).
In initial pilot studies, we found object identification via bounding boxes to be problematic.
In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the box (for instance, for a box around a jacket, the man wearing it).
We took special care of minimizing this issue in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning the set of images via an initial collection round (9 workers per task, i.e.,\ 9 names/object) in which we allowed workers to indicate whether the object was occluded or the box unclear (see Figure~\ref{fig:instructions1} for the instructions).

%We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images.
After the first round, based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection): (i) they were not marked as occluded by any subject; (ii) ``Bounding box is unclear'' was marked at most twice; (iii) at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects); (iv) the most frequent elicited name is of the same domain as the \vgenome name.
This yielded $25,596$ images (we discarded $5,497$).
We then did 3 more collection rounds, shuffling the set of images per task between each round.
Figure~\ref{fig:instructions2} shows the instructions for these rounds; they were accompanied by a FAQ solving common issues. 
Workers could only participate in one round, to avoid workers annotating an instance more than once. 
We obtained a total of 36 names per object.
Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.

>>>>

\begin{table*}[htp]
	\small
	\centering
	\begin{tabular}{lp{14cm}}
			\toprule
			Domain & \multicolumn{1}{c}{Collection synsets}\\
			\midrule			
			animals\_plants & ungulate$_1$ (2037), horse$_1$ (833), feline$_1$ (763), dog$_1$ (688)
			bird$_1$ (389), flower$_1$ (44), rodent$_1$ (27), insect$_1$ (12), fish$_1$ (11)\\
			buildings      &  house$_1$ (364), bridge$_1$ (297), shelter$_1$ (169), restaurant$_1$ (58),
                                         outbuilding$_1$ (31), hotel$_1$ (19), housing$_1$ (17), place\_of\_worship$_1$ (12)     \\
			clothing       &  shirt$_1$ (968), overgarment$_1$ (786), dress$_1$ (199), headdress$_1$ (135),
                                         neckwear$_1$ (65), robe$_1$ (27), glove$_2$ (7), footwear$_1$ (5)    \\
			food           &  dish$_2$ (812), baked\_goods$_1$ (770), foodstuff$_2$ (280), vegetable$_1$ (48),
                                         edible\_fruit$_1$ (42), beverage$_1$ (23)   \\
			home           &  furnishing$_2$ (5,355), vessel$_3$ (525), kitchen\_utensil$_1$ (132), crockery$_1$ (92),
			cutlery$_2$ (82), tool$_1$ (72), lamp$_1$ (34)    \\
			people         & woman$_1$ (1768), man$_1$ (1167), male\_child$_1$ (853), athlete$_1$ (396),
			 child$_1$ (333), creator$_2$ (11), professional$_1$ (5)    \\
			vehicles       &  aircraft$_1$ (1208), train$_1$ (957), car$_1$ (727), motorcycle$_1$ (564),
                                         truck$_1$ (559), boat$_1$ (499), ship$_1$ (38)    \\
			\bottomrule
		\end{tabular}
		\caption{Overview of the ManyNames dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses).
                  \label{tab:overview_dataset2}}
	\end{table*}

@@

We take data from \vgenome~\cite{krishna2016visualgenome}, which
contains a dense region-based labeling of $108$K~images with, inter alia, object names, attributes and relationships,
all linked to WordNet synsets \cite{fellbaum1998wordnet}.
\vgenome (VG) suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
As common in Computer Vision, objects are localized as bounding boxes, as in Figure~\ref{fig:cake}.% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

@@

%Criteria: From CV: select images depicting objects with relatively frequent names; From CogSci: select objects which have been frequently studied in cognitive science/psychological norming studies; we chose McRae et al. as basis.
We selected images from seven domains: \domain{animals\_plants}, \domain{buildings}, \domain{clothing}, \domain{food}, \domain{home}, \domain{people}, \domain{vehicles}. 
They are all based on McRae et al.'s  \cite{mcrae2005semantic} feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories, except for \domain{people}, which we added because it is a very frequent category in \vg and a very prominent category for humans.
% We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\domain{animals}, \domain{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
% We added the \domain{person} category because it is very frequent category in \vgenome.

Within each domain, we aimed at collecting instances at different taxonomic levels to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy in the first place (e.g.\ \domain{home}).
Instead, we defined a set of synsets ($52$\ in total; listed in Table~\ref{tab:overview_dataset2}) that we used to collect object instances from \vg, as follows.

From the set of synsets that match or subsume the concepts in the McRae norms, we kept those with a high number of \vg object instances of different names.
For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
%\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}

We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds} ($450$\ in total).
%\gbt{from the dataframe it's 449. Also, there are some mistakes ('dugout.', 'man's').+++
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.} 
% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
% \paragraph{Sampling of instances}
Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds. This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as explained next.
Table~\ref{tab:overview_dataset1} shows the top 5 \vgenome names in each of the domains.

@@

To elicit object names, we set up a crowdsourcing task on Amazon Mechanical Turk (AMT).
In initial pilot studies, we found object identification via bounding boxes to be problematic.
In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the box (for instance, for a box around a jacket, the man wearing it).
We took special care of minimizing this issue in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning images with unclear boxes or occluded objects via an initial collection round in which we allowed workers to mark such cases.
Figure~\ref{fig:instructions1} shows the task instructions for this first round, in which 9 workers annotated each image.

%We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images.
After the first round, and based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection): (i) they were not marked as occluded by any subject; (ii) ``Bounding box is unclear'' was marked at most twice; (iii) at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects); (iv) the most frequent elicited name is of the same domain as the \vgenome name.
This yielded $25,596$ images (we discarded $5,497$).
We then did 3 more collection rounds, obtaining a total of 36 images per object.
Figure~\ref{fig:instructions2} shows the instructions for these rounds; they were accompanied by a FAQ solving common issues. 
We shuffled the set of images per task between rounds, and workers could only participate in one round, to avoid workers annotating an instance more than once.
Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.

### 2019-11-25 papers/LREC2020/lrec2020naming.tex
some changes towards the LREC submission
Section 4 - data collection polished

\newcommand{\refexp}[1]{\textsl{#1}}
\newcommand{\word}[1]{\textsl{#1}}
\newcommand{\cat}[1]{\textsc{#1}}
\newcommand{\vgenome}{VisualGenome\xspace}
\newcommand{\vg}{VG\xspace}
\newcommand{\ra}{$\rightarrow$}
\newcommand{\referit}{ReferIt\xspace}
\newcommand{\refcoco}{RefCOCO\xspace}
\newcommand{\refcocop}{RefCOCO+\xspace}
\newcommand{\flickr}{Flickr30k Entities\xspace}

@@

%\title{Naming Objects in Real-world Images: A survey and A new \sz{linguistically motivated????} collection}
\title{Object Naming: A Survey and a New Dataset}

@@

\abstract{
Massive data collections for applications in language \& vision are nowadays available. In principle, these could constitute valuable resources also for research in computational linguistics (CL), besides task-specific modeling. However, in practice, very few studies have tested linguistic hypotheses using these large-scale datasets. In this paper, we illustrate the challenges of using this type of corpora for CL research, by focusing on a case study, namely naming of objects in real-world images. Our analysis of existing resources in language \& vision reveals that available datasets do not generally provide the right type and consistent quality of object naming data,  for being able to conduct a linguistically motivated study of this phenomenon. We contribute a new dataset on top of Visual Genome that  \sz{... continue}
 \\ \newline \Keywords{keyword1, keyword2, keyword3} }

@@

\section{Object Names in Existing L\&V resources}
\input{survey}

@@

% \section{Acknowledgements}

>>>>

\newcommand{\refexp}[1]{\textsl{#1}}
\newcommand{\word}[1]{\textsl{#1}}
\newcommand{\cat}[1]{\textsc{#1}}
\newcommand{\domain}[1]{\textsc{#1}}
\newcommand{\vgenome}{VisualGenome\xspace}
\newcommand{\vg}{VG\xspace}
\newcommand{\ra}{$\rightarrow$}
\newcommand{\referit}{ReferIt\xspace}
\newcommand{\refcoco}{RefCOCO\xspace}
\newcommand{\refcocop}{RefCOCO+\xspace}
\newcommand{\flickr}{Flickr30k Entities\xspace}

@@

\title{Object Naming in Language and Vision: A Survey and a New Dataset}

@@

\abstract{
People choose particular names for objects, such as \word{dog} or \word{puppy} for a given particular dog.
Object naming has been studied in Psycholinguistics, but has received relatively little attention in Computational Linguistics (CL).
We review resources from Language and Vision that could be used to study object naming on a large scale, discuss their shortcomings, and create a new dataset that affords more opportunities for analysis and modeling.
Our dataset, ManyNames, provides 36 name annotations for each of 25K images from VisualGenome.
We highlight the challenges involved and provide a preliminary analysis of the ManyNames data that, on the one hand, shows high consistency in naming, and on the other, suggests that the main source of variation analyzed to date (taxonomic variation, as in \word{chihuahua} vs.\ \word{dog}) may not be the main driver of diversity in naming behavior, at least in our setup.
% , contrary to expectation, hierarchical variation is not the main source of 
% Massive data collections for applications in language \& vision are nowadays available. In principle, these could constitute valuable resources also for research in computational linguistics (CL). However, in practice, very few studies have tested linguistic hypotheses using these large-scale datasets. In this paper, we illustrate the challenges of using this type of corpora for CL research, by focusing on a case study, namely naming of objects in real-world images. Our analysis of existing resources in language \& vision reveals that available datasets do not generally provide the right type and consistent quality of object naming data,  for being able to conduct a linguistically motivated study of this phenomenon. We contribute a new dataset on top of Visual Genome that  \sz{... continue}
 \\ \newline \Keywords{object naming, language and vision, computer vision} }

@@

\section{Object Names in Existing L\&V resources}
\label{sec:survey}
\input{survey}

@@

 \section{Acknowledgements}

### 2019-11-25 papers/LREC2020/survey.tex
Section 4 - data collection polished

We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome. Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{+++}). 
As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to examine naming variation.
This motivates our data collection, in which we collect 36 names per object.
Still, because these datasets can be useful to examine other aspects of object naming, and we summarize their characteristics below.

\begin{table*}
\centering
\begin{tabular}{lrrrrr}
\toprule
  &   RefCoco/+  &  Flickr30kE &           VG &      VGmn &        MN \\
\midrule
                  \# objects & 50.000 & 243.801 & 3.781.232 & 25.223 & 25.315 \\
                naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
     av. annotations/object &      2.84 &       2.30 &         1.69 &      7.24 &     35.30 \\
 \% objects with n types $>$ 1 &      0.68 &       0.29 &         0.02 &      0.05 &      0.93 \\
           av. types/object &      1.88 &       1.38 &         1.02 &      1.08 &      5.70 \\
\bottomrule
\end{tabular}
\label{tab:compare}
\caption{Overview statistics for different data sets containing object naming data \gbt{What is the VGmn column? Is it necessary?}}
\end{table*}

@@

Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO \cite{mscoco}, 
%The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
%However, the COCO region-level (object) annotations are not linked to the captions.
a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects. \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories? How did you compute these numbers, are they for names, or whole REs?}
% Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.

>>>>

We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome. Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{sec:data}).
As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to examine naming variation.
This motivates our data collection, in which we collect 36 names per object.
Still, because these datasets can be useful to examine other aspects of object naming, and we summarize their characteristics below.

\begin{table*}
\centering
\begin{tabular}{lrrrrr}
\toprule
  &   RefCoco/+  &  Flickr30kE &           VG &      VGmn &        MN \\
\midrule
                  \# objects & 50.000 & 243.801 & 3.781.232 & 25.223 & 25.315 \\
                naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
     av. annotations/object &      2.84 &       2.30 &         1.69 &      7.24 &     35.30 \\
 \% objects with n types $>$ 1 &      0.68 &       0.29 &         0.02 &      0.05 &      0.93 \\
           av. types/object &      1.88 &       1.38 &         1.02 &      1.08 &      5.70 \\
\bottomrule
\end{tabular}
\label{tab:compare}
\caption{Overview statistics for different data sets containing object naming data \gbt{What is the VGmn column? Is it necessary?} \sz{VGmn refers to the subset of images in VG that appear in MN. This shows that the images we selected for ManyNames also have more annotations in VG. I think this is useful to know.}}
\end{table*}

@@

Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO \cite{mscoco}, 
%The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
%However, the COCO region-level (object) annotations are not linked to the captions.
a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects. \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories? How did you compute these numbers, are they for names, or whole REs?} \sz{well, 80 categories doesn't mean much as the categories can be very general (like "human") ... and it nicely shows that natural names are much more variable than strict categories}
% Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.
